Grip strength, mating success, and immune and energy costs in a population sample of US women and men: a registered report

### 2024-03-25 paper.v2.qmd
changes from switching to visual mode

The aim of this study is to replicate the costs and benefits of formidability reported by @@lassek2009 using similar nationally representative data, controlling for a wider range of possible confounds, and precisely prespecifying the statistical models in a registered report format. It also aims to investigate if these costs and benefits are also experienced by women.

@@

We first derived a simple model based on that reported in Table 2 in @lassek2009 for each outcome measure (total number of partners, past year number of partners, and age at first intercourse) predicted by age, sex, grip strength, and partnered status. This model also includes an anthropometric control, body mass index (BMI), calculated as kg/m^2, since body size could impact either strength or mating outcomes. We interacted age, strength, and BMI with sex to assess differences in these predictors for men and women.

@@

# Confirmatory Analysis [not yet conducted]

>>>>

The aim of this study is to replicate the costs and benefits of formidability reported by \@@lassek2009 using similar nationally representative data, controlling for a wider range of possible confounds, and precisely prespecifying the statistical models in a registered report format. It also aims to investigate if these costs and benefits are also experienced by women.

@@

We first derived a simple model based on that reported in Table 2 in @lassek2009 for each outcome measure (total number of partners, past year number of partners, and age at first intercourse) predicted by age, sex, grip strength, and partnered status. This model also includes an anthropometric control, body mass index (BMI), calculated as kg/m\^2, since body size could impact either strength or mating outcomes. We interacted age, strength, and BMI with sex to assess differences in these predictors for men and women.

@@

# Confirmatory Analysis \[not yet conducted\]
